How to Discourage Useless Refactorings

### 2016-08-18 Manuscript.tex
Updates from ShareLaTeX

\title{How to Stop Useless Refactorings}

@@

\begin{abstract} 
{\bf Context: } 
Developers use code bad smells to gudie their refactoring (reorganizing their code).
Yet developers, text books, and tools disagree on which bad smells are important.
%Many bad smell detectors recommend refactoring when static code measure
%cross some threshold boundary. 
%%However, it is unclear at what threshold values smell-related metrics
%should trigger code improvement or preventative maintenance.

\noindent 
{\bf Objective: } We seek to a tool that can recognize  useless refactorings.

\noindent
{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, generates
a set of useful code changes.
Any bad smell that requires changes outside of that set can be deprioritized 
(since there is no
historical evidence that that bad smell causes any problems).

@@

Note that these managers are {\em not} asking for better
automatic refactoring
tool support. Their human programmers are refactoring
code all the time, perhaps too much so.
Hence, their management goal is: 
\bi
\item
{\em Not} to optimize {\em necessary} refactorings;
\item
But rather to stop {\em unnecessary} refactorings.
\ei
For those managers, we offer the  following heuristic:
\bi
\item If there is no evidence in the historical record that changing ``X'' is useful;
\item Then stop developers from doing ``X''.
\ei
This paper describes one way to operationalize this heuristic, in the context
of assessing bad smells. We use data mining to generate two oracles: a {\em primary
change oracle} and a {\em secondary verification oracle}.
By combining these two oracles,
 we can generate and validate useful
changes to code modules.

In this paper, we use 
the XTREE cluster delta algorithm as the {\em primary change  oracle} .
XTREE 
explores the historical record of a project to find clusters of projects.
It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
is some subset of $C_1 - C_0$). To define ``minimal'', XTREE uses an entropy measure.

As to 
the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we use Random Forests\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task to learning the primary
oracle. This  ensures that the verification oracle offers an independent
opinion on the value of the proposed changes.

@@

This paper  claims that (a)~XTREES is a  better way than \eq{fd}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since usually refer to a very 
small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
static code measures). 
In support of these claims, 
the rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
  in Section~3, 
  different methods for determining when code does/does not have bad smell. One of those methods
  will be XTREE while the others will come from other researchers. Next,    Section~4
  defines an assessment method that checks which of these methods is most useful. The results from that assessment 
  are presented in Section~5. Those results will answer five research questions.

@@

 {\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. effect fewest attributes) then those changes
will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
code attributes?
\begin{lesson}
Of all the code change oracles studied here, XTREE recommend  far fewest changes to static code measures.
\end{lesson}

 {\bf RQ3: Stopping}: Our advice to managers is to stop refactoring based on changes that lack
historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
\begin{lesson}
In  any  project,  XTREE’s  recommended  changes  only  mentions one to four 
of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
would hence be deprecated.
\end{lesson}

@@

{\bf RQ5: Conjunctive Fallacy}:  
Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
\begin{lesson}
XTREE usually recommends reducing lines of code (size of the modules).
That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
\end{lesson} 
Note that {\bf RQ3, RQ4, RQ5} 
confirms the intuitions
of the project managers that prompted this investigation:
\bi
\item
Yes,  indeed, their programmers
were wasting time on   performing refactorings  that  decreased multiple measures when, in fact,
they should be trying to {\em decrease} some measures while {\em increasing} others.
\item
Across all studied projects, XTREE found that  around one-fifth  
  of the measures were usually found within  change recommendations. That is, it is 80\% likely that
  that refactoring based on reducing any one measurement picked at random will be useful.
\ei
Consequently, we  recommend the following use case for  XTREE:
\bi
\item Before doing  refactoring based on a bad smell report...
\item ...check and stop any refactoring   for which there is no proof
  in the historical record that that change improves the code.
\ei
This use case described  applies to both manual refactorings proposed by developers
as well as refactoring as conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
code refactoring by discouraging refactorings for useless goals.

@@

The results of this paper care biased by out choice of refactoring goal (reducing defects) and our choice
of measures collected from software project (OO measures such as
  depth of inheritance, number of child classes, etc).

  That said, it should be possible extend the methods of this paper to  other kinds of other kinds of goals (e.g. maintainability, reliability, security,
  or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
  \bi
  \item Find a data source for the other measures of interest;
  \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
\item Implement a better primary verification oracle that can do ``better'' that XTREES at finding changes (where ``better'' is defined in terms 
of the opinions of the verification oracle).
\ei
To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.

@@

The recommendation to management, shown on page one of this paper,  was to stop developers doing ``X'' if there was
nothistorical evidence that ``X'' was useful. 
This recommendation assumes that such an  historical record can be accessed. If not,  then the results of this paper could be use used as a guide (see our Table 8). Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).

  \subsection{Relationship to Prior Work }
A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
the five data sets studied here. Also, that prior work had:
\bi
\item
no comparison to any baseline
method from other researchers, whereas this paper compares XTREE's recommendations
with those found by researchers exploring bad smells.
\item
no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
\ei
Further, of this entire paper, the only sections containing material
found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{jur}.

@@

If the above remarks hold true for bad smells, then we would expect
to see much disagreement on which bad smells are important and relevant
to  a particular project. This is indeed the case.
The first column of \fig{smells} 
lists  commonly mentioned bad smells and comes from Fowler's 1999 text~\cite{fowler99} and a subsequent 2005 text by Kerievsky that is widely cited~\cite{Kerievsky2005}.
The other
columns show data from other studies on which bad smells matter most.
The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column maked SonarQube is a popular open source
code assessment tool that includes detectors for six of the bad smells
in column one. 
The {\em developer survey}   (in the right-hand-side column),
  this shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
    D.C. web tools development company. Participants
    worked in a round robin manner to rank the bad smells they thought were
    important (and any disagreements were discussed with the whole group).
     Amongst the group, there was  some
    consensus on  the priority of which bad smells to fix
    (see the annotations VH=very high,
    H=high, L=low, VL=very low, and ``?''= no consensus).

@@

A  blank cell in \fig{smells}
indicates where   other work has chosen to ignore
one the   bad smells in column one. 
Note that most of the cells are blank, and that the studies ignore the majority of the Fowler bad smells.
SonarQube has no detectors for many of the column one bad smells.
Also, nearly half the Yamashita list of bad smells
    does not appear in the Fowler and Kerievsky list. The eight numbers
    in the  Yamashita'13 column show the rankings for the bad smells 
    that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99.

@@

The SE literature offers  two ways to 
learning bad smell thresholds.
One approach relies on 
{\em outlier statistics}~\cite{erni96,bender99}. This approach
has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
    and Hermans et al.~\cite{hermans15}.
    Another approach is 
    based on {\em cluster deltas} that we developed
    for   Centroid Deltas~\cite{me12c} and 
    use here for XTREE. 
    These two approaches are discussed below.

The outlier approach assume that unusually large measurements indicate risk-prone code.
Hence, they generate one bad smell threshold for any metric
with such an ``unusually large'' measurements. 
The literature lists several ways to define ``unusually large''.

@@

\subsubsection{Enri \& Lewerentz}
Given classes described with the  code metrics of \fig{ck},
Enri and Lewerentzz~\cite{erni96} found the   mean $\mu$ and the standard deviation $\sigma$
of each
code metrics. Their definition of problematic outlier was any code
metric with a measurement greater than $\mu+\sigma$.
Shatnawi and Alves et al.~\cite{Shatnawi10,Alves2010} depreciate
using $\mu+\sigma$ since it does not consider the fault-proneness of classes when the thresholds are computed. Also, the method lacks  empirical verification.

@@

\begin{figure*}[!t]
~\hrule~
\begin{minipage}{.53\linewidth}
\small
 \begin{tabular}{p{0.95\linewidth}} 
 On the right-hand-side is a tree
 generated by iterative dichomization. 
 This tree can be read like a nested if-then-else statement; e.g.
 \begin{itemize}
     \item Lines 3 and 8 show two branches for lines of code (denoted here as {\em `\$loc}) below 698 and above 698.
     \item Any line with a colon ":" character shows  a  leaf  of  this  nesting.   For  example,  if  some  new  code module is passed down this tree and falls to the line marked in \textcolor{orange}{{\bf orange}},  the colon on that line indicates a prediction that this module has a 100\% chance of being defective. 
     \end{itemize}
Using this tree,
 XTREE looks for a nearby branch that has a lower chance of being defective. Finding the \textcolor{green}{{ green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{ green}} designed branch. 
 In this case, that threshold relates to:
 \begin{itemize}
     \item Lines of code and comments ({\em lcom}) 
     \item The cohesion between classes ({\em cam}) which measures similarity of parameter lists to assess the relatedness amongst class   methods.
     \end{itemize}\\ 
 \end{tabular}
 \end{minipage}~~~~
 \begin{minipage}{.45\linewidth}
\includegraphics[width=\linewidth]{figs/XTREE_samp.png}
\end{minipage}
~\hrule~
 \caption{A brief tutorial on XTREE.} \label{fig:xtree_samp}
\end{figure*}

\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction fallacy}  discussed in the introduction.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what minimal
metrics need to be changed at the same time (or whether or not those
changes need to minimizations or maximations of static code measures).

@@

Hence our {\bf Result3} is that, in a any  project,  XTREE’s  recommended  changes  only  mentions one to four 
of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
would hence be deprecated.

@@

% of ``better'' deefined as per \eq{fd} is misleading.

@@

% % The main internal validity threat   in this study was the use of
% % optimistic reasoning when generating the changed code modules.
% We assumed in \tion{rq}
% that any code module can be changed in order
% to stop triggering a bad smell detector. This is not necessarily
% true, as noted in {\em PROBLEM \#2} in this paper's introduction.
% To mitigate this issue:
% \begin{itemize}
%     \item We do not propose using XTREE as a bad
% smell generator;
% \item Rather, we offer it as  a critique agent for bad smells
% proposed by some other oracle (e.g. a human developer).
% \end{itemize}
% We showed about that XTREE's recommendations are not verbose.
% That is, even if XTREE recommends the superset of possibly important bad smells,
% that superset is not so large as to  overlap with many
%  bad smell proposed at random 
% by   developers.

@@

\section{Conclusions}
How to stop useless refactorings?
We say: ignore those not supported by the historical log of data from
the current project.  
When that data is not available (e.g. early
in the project) then developers could use the general list of
bad smells shown in \fig{smells}. However, 
our results
show that  bad smell detectors are most
effective when they are based
on a small handful of code metrics (as done by XTREE).
Hence, using all the bad smells of \fig{smells} may not be optimal.

>>>>

\title{How to Discourage Useless Refactorings}

@@

\begin{abstract} 
{\bf Context: } 
Developers use code bad smells to guide their refactoring (reorganizing their code).
Yet developers, text books, and tools disagree on which bad smells are important.
%Many bad smell detectors recommend refactoring when static code measure
%cross some threshold boundary. 
%%However, it is unclear at what threshold values smell-related metrics
%should trigger code improvement or preventative maintenance.

\noindent 
{\bf Objective: } We seek to introduce a tool that can recognize  useless refactorings.

\noindent
{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, generates
a set of useful code changes.
Any bad smell that requires changes outside of that set can be deprioritized 
(since there is no
historical evidence that the bad smell causes any problems).

@@

Note that these managers are {\em not} asking for better
automatic refactoring
tool support. Their human programmers are refactoring
code all the time, perhaps too much so.
Hence, their management goal is: 
\bi
\item
{\em Not} to optimize {\em necessary} refactorings;
\item
But rather to discourage {\em unnecessary} refactorings.
\ei
For those managers, we offer the  following heuristic:
\bi
\item If there is no evidence in the historical record that changing ``X'' is useful;
\item Then discourage developers from doing ``X''.
\ei
This paper describes one way to operationalize this heuristic, in the context
of assessing bad smells. We use data mining to generate two oracles: a {\em primary
change oracle} and a {\em secondary verification oracle}.
By combining these two oracles,
 we can generate and validate useful
changes to code modules.

In this paper, we use 
the XTREE cluster delta algorithm as the {\em primary change  oracle}.
XTREE 
explores the historical record of a project to find clusters of projects.
It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.

As to 
the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
sensible changes. For this purpose we use Random Forest\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
 In our framework,  learning
the secondary oracle is   a {\em separate} task from that of learning the primary
oracle. This  ensures that the verification oracle offers an independent
opinion on the value of the proposed changes.

@@

This paper  claims that (a)~XTREES is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very 
small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
static code measures). 
In support of these claims, 
the rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
  in Section~3, 
  different methods are presented for determining when code does/does not have bad smell. One of those methods
  will be XTREE while the others will come from other researchers. Next,    Section~4
  defines an assessment method that checks which of these methods is most useful. The results from that assessment 
  are presented in Section~5. Those results will answer five research questions.

@@

 {\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. affect fewest attributes) then those changes
will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
code attributes?
\begin{lesson}
Of all the code change oracles studied here, XTREE recommend  far fewest changes to static code measures.
\end{lesson}

 {\bf RQ3: Stopping}: Our advice to managers is to discourage refactoring based on changes that lack
historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
\begin{lesson}
In  any  project,  XTREE's  recommended  changes  only  mentions one to four 
of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
would hence be deprecated.
\end{lesson}

@@

{\bf RQ5: Conjunctive Fallacy}:  
Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
\begin{lesson}
XTREE usually recommends reducing lines of code (size of the modules).
That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
\end{lesson} 
Note that {\bf RQ3, RQ4, RQ5} 
confirms the intuitions
of the project managers that prompted this investigation:
\bi
\item
Yes,  indeed, their programmers
were wasting time on   performing refactorings  that  decreased multiple measures when, in fact,
they should be trying to {\em decrease} some measures while {\em increasing} others.
\item
Across all studied projects, XTREE found that  around one-fifth  
  of the measures were usually found within  change recommendations. That is, it is 80\% likely that
  that refactoring based on reducing any one measurement picked at random will be useful.
\ei
Consequently, we  recommend the following use case for  XTREE:
\bi
\item Before doing  refactoring based on a bad smell report...
\item ...check and discourage any refactoring   for which there is no proof
  in the historical record that the change improves the code.
\ei
This use case described  applies to both manual refactorings proposed by developers
as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
code refactoring by discouraging refactorings for useless goals.

@@

The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
of measures collected from software project (OO measures such as
  depth of inheritance, number of child classes, etc).

  That said, it should be possible extend the methods of this paper to other kinds of goals (e.g. maintainability, reliability, security,
  or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
  \bi
  \item Find a data source for the other measures of interest;
  \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
\item Implement a better primary verification oracle that can do ``better'' that XTREE at finding changes (where ``better'' is defined in terms 
of the opinions of the verification oracle).
\ei
To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.

@@

The recommendation to management, shown on page one of this paper,  was to discourage developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
This recommendation assumes that such an  historical record can be accessed. If not,  then the results of this paper could be use used as a guide (see our Table 8). Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).

  \subsection{Relationship to Prior Work }
A four page preliminary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies on only two  of
the five data sets studied here. Also, that prior work had:
\bi
\item
no comparison to any baseline
method from other researchers, whereas this paper compares XTREE's recommendations
with those found by researchers exploring bad smells.
\item
no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
\ei
Further, of this entire paper, the only sections containing material
found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{jur}.

@@

If the above remarks hold true for bad smells, then we would expect
to see much disagreement on which bad smells are important and relevant
to  a particular project. This is indeed the case.
The first column of \fig{smells} 
lists  commonly mentioned bad smells and comes from Fowler's 1999 text~\cite{fowler99} and a subsequent 2005 text by Kerievsky that is widely cited~\cite{Kerievsky2005}.
The other
columns show data from other studies on which bad smells matter most.
The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column maked SonarQube is a popular open source
code assessment tool that includes detectors for six of the bad smells
in column one. 
The {\em developer survey} (in the right-hand-side column) shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
    D.C. web tools development company. Participants
    worked in a round robin manner to rank the bad smells they thought were
    important (and any disagreements were discussed with the whole group).
     Amongst the group, there was  some
    consensus on  the priority of which bad smells to fix
    (see the annotations VH=very high,
    H=high, L=low, VL=very low, and ``?''= no consensus).

@@

A  blank cell in \fig{smells}
indicates where   other work has chosen to ignore
one of the bad smells in column one. 
Note that most of the cells are blank, and that the studies ignore the majority of the Fowler bad smells.
SonarQube has no detectors for many of the column one bad smells.
Also, nearly half the Yamashita list of bad smells
    does not appear in the Fowler and Kerievsky list. The eight numbers
    in the  Yamashita'13 column show the rankings for the bad smells 
    that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99.

@@

The SE literature offers two ways of learning bad smell thresholds.
One approach relies on 
{\em outlier statistics}~\cite{erni96,bender99}. This approach
has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
    and Hermans et al.~\cite{hermans15}.
    Another approach is 
    based on {\em cluster deltas} that we developed
    for   Centroid Deltas~\cite{me12c} and 
    use here for XTREE. 
    These two approaches are discussed below.

The outlier approach assume that unusually large measurements indicate risk-prone code.
Hence, they generate one bad smell threshold for any metric
with such an ``unusually large'' measurement. 
The literature lists several ways to define ``unusually large''.

\input{xtree_tut.tex}

@@

\subsubsection{Enri \& Lewerentz}
Given classes described with the  code metrics of \fig{ck},
Enri and Lewerentz~\cite{erni96} found the   mean $\mu$ and the standard deviation $\sigma$
of each
code metrics. Their definition of problematic outlier was any code
metric with a measurement greater than $\mu+\sigma$.
Shatnawi and Alves et al.~\cite{Shatnawi10,Alves2010} depreciate
using $\mu+\sigma$ since it does not consider the fault-proneness of classes when the thresholds are computed. Also, the method lacks  empirical verification.

@@

\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction fallacy}  discussed in the introduction.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what minimal
metrics need to be changed at the same time (or whether or not those
changes lead to minimization or maximization of static code measures).

@@

Hence our {\bf Result3} is that, in a any  project,  XTREE's  recommended  changes  only  mentions one to four 
of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
would hence be deprecated.

@@

% of ``better'' deefined as per \eq{df} is misleading.

@@

% % The main internal validity threat   in this study was the use of
% % optimistic reasoning when generating the changed code modules.
% We assumed in \tion{rq}
% that any code module can be changed in order
% to discourage triggering a bad smell detector. This is not necessarily
% true, as noted in {\em PROBLEM \#2} in this paper's introduction.
% To mitigate this issue:
% \begin{itemize}
%     \item We do not propose using XTREE as a bad
% smell generator;
% \item Rather, we offer it as  a critique agent for bad smells
% proposed by some other oracle (e.g. a human developer).
% \end{itemize}
% We showed about that XTREE's recommendations are not verbose.
% That is, even if XTREE recommends the superset of possibly important bad smells,
% that superset is not so large as to  overlap with many
%  bad smell proposed at random 
% by   developers.

@@

\section{Conclusions}
How to discourage useless refactorings?
We say: ignore those not supported by the historical log of data from
the current project.  
When that data is not available (e.g. early
in the project) then developers could use the general list of
bad smells shown in \fig{smells}. However, 
our results
show that  bad smell detectors are most
effective when they are based
on a small handful of code metrics (as done by XTREE).
Hence, using all the bad smells of \fig{smells} may not be optimal.
